### 2021-07-09 doc/thesis/chapters/system-architecture-and-concept.tex
write stuff
text update

%%%%%%%%%%%%%%%%%%%%
\chapter{System Architecture/Concept}
\label{cha:SystemArchitecture/Concept}

  \section{Block Diagram (with details)}
    \subsection{describe blocks}

  \section{Which parts in HLS and VHDL}

  \section{Test Environment}

>>>>

%%%%%%%%%%%%%%%%%%%%
\chapter{System Architecture and Concept}
\label{cha:SystemArchitectureAndConcept}

This chapter introduces the FM radio receiver project that is implemented as a major part of this thesis.
It specifically talks about the system level approach that is taken in the implementation of the project.
The main concept, as well as the architecture are explained.

%%%%%%%%%%%%%%%%%%%%
\section{Overview}

In the development of a project that includes multiple functional parts, it is always of advantage to start with a system level overview.
Major decisions can be made at this stage, before any implementation has begun.
This can have a direct impact on the efficiency of the entire development, which concequently has an impact on the final quality of the product.
A thorough system level design can also prevent from issues that would otherwise arise while the development is already ongoing.
As an example it could turn out that one of the functional parts is not able to fit into the integrated system, in the way it is implemented.
This leads to the necessity to re-engineer this entire functional block.
As a result, it takes more effort to implement the functionality, which directly correlates with the development cost and the time-to-market, in order to deliver the final product.
Summing up, a comprehensive system level architecture and concept can pave the way for a successful implementation of a project from start to finish.\\

In order to create a system level design, considerations around the high-level, final goal of the product are a good starting point.
This includes the definition of its functional range.
Once this is done, the target system or target hardware should be considered, because there are various ways to implement a certain functionality.
All of these variants will eventually result in the same output, but will, however, heavily differ in their implementation effort, efficiency, or their applicability for the products' aim in general.
Thus, things like the available hardware platform, implementation time, degree of optimization, output quality, and similar things are important factors at this stage.
Of course, there are many more factors to consider when a product is to be developed.
However, only a subset of these is covered here, since this chapter is focused on how this thesis' accompanying project was developed and is thus written in that context.\\

%%%%%%%%%%%%%%%%%%%%
\section{The project}

The aim of this thesis is to implement an FM radio receiver in multiple different methods and ways of implementation.
The final goal thereby is always be the same, that is: Listen to the music of a radio station that is transmitted over FM broadcast radio.

In the context of a system level design approach, several steps are necessary to find a solution that is ready to be implemented.
As a very first step, the inner workings of an FM receiver need to be understood.
This mainly regards the signal processing theory, to be able to decode the signal that is received by the antenna.
Chapter \ref{cha:SignalProcessingTheory} describes this part into detail.

As already mentioned above, multiple ways of technology and implementation can lead to a similar result.
Thus, the next step is to define a set of possible ways, which will actually be implemented.
For this thesis, the decision was made to implement the FM radio receiver, using the following methods.

\begin{itemize}
  \item \textbf{GNU Radio} \cite{GnuRadio}\\
      GNU Radio is a free and open-source software development toolkit to implement a software-defined radio. The implementation is done by connecting functional blocks in a block design. This abstracts the inner workings of each functional block and thus provides an implementation approach on a very high level of abstraction.
  \item Matlab
  \item FPGA: \cplusplus High-Level Synthesis
  \item FPGA: VHDL
\end{itemize}

Once the basic theory is understood, implementation can begin.

% list of variants
%-  implementation of a model and DSP concept in Matlab \\
%-  implementation in VHDL and HLS \\
%-  both use the same testbench source \\
%-  both are integrated into FPGA
%-  the FPGA output is read back into the firmware, for analysis \\

%%%%%%%%%%%%%%%%%%%%
\section{Block Diagram (with details)}
%%%%%%%%%%%%%%%%%%%%
\subsection{describe blocks}

%%%%%%%%%%%%%%%%%%%%
\section{Test Environment}
